### 2015-03-02 fundamentals/impl.tex
addresses Erich's comment that ' difference between manual and lazy is not clear to me.  Specifically, what's the difference between 'decay as needed' and 'decay whenever queried'?'

    \item "manual" (currently implemented) is the default mode
        where agents decay materials as needed,

    \item "never" (currently implemented) globally turns off all decay.
        The Material decay function does nothing,

    \item "lazy" (currently implemented) decays any material whenever its
        composition is observed (e.g. when an agent queries information about
        a material's $^{239}$Pu content),
    \item "periodic" (future) automatically decays all materials in a
        simulation with some fixed frequency.

>>>>

\begin{itemize}
    \item "manual" (currently implemented) is the default mode
        where agents decay materials when requested by an archetype,
    \item "never" (currently implemented) globally turns off all decay.
        The Material decay function does nothing,
    \item "lazy" (currently implemented) decays material automatically whenever
         its composition is observed (e.g. when an agent queries information
         about a material's $^{239}$Pu content),
    \item "periodic" (future) automatically decays all materials in a
        simulation with some fixed frequency.
\end{itemize}
